First exclusive DVCS measurement off bound nucleon in $^4$He

### 2018-02-19 eg6-letters/incoherent/incoherent_prl.tex
1st set of implementing the comments from Stepan

%
\begin{document}
%\linenumbers

\title{Revealing the Bound Nucleon 3D Partonic Structure through Incoherent 
Deeply Virtual Compton Scattering off $^4$He}

@@

%
\date{\today}
\begin{abstract}
We report on the beam-spin asymmetries associated with incoherent deeply 
   virtual Compton scattering off $^4$He in the valence quark region.  The data 
   have been accumulated using a 6 GeV longitudinally-polarized electron beam 
   incident on a pressurized $^4$He gaseous target placed in front of the CLAS 
   spectrometer in Hall-B at Thomas Jefferson National Accelerator Facility.  
   The baseline detection sub-systems of CLAS detected the scattered electrons 
   and the recoil protons, while the final-state real photons are detected by a 
   supplementary electromagnetic calorimeter at very forward angles. The 
   measured beam-spin asymmetries on bound-protons exhibit a suppression 
   compared to those on free proton, indicating possible medium modifications 
   on the nucleon's quark distributions and opening new opportunities to 
   explore the origin of the EMC effect within the framework of the generalized 
   parton distributions.

@@

Electromagnetic probes have played a major role in advancing our knowledge 
about the structure of nucleons, which are the origin of almost all the
Universe visible matter. While the elastic lepton-nucleon measurements have 
taught us about the spatial charge and magnetization distributions 
\cite{Hofstadter:1955ae,Perdrisat:2006hj}, the deep-inelastic scattering (DIS) 
experiments have uncovered the features of momentum sharing between the 
constituents partons, i.e., quarks and gluons \cite{Dokshitzer:1977sg,pdg}. 
With nuclear targets, the DIS measurements have revealed the fact that the 
distribution of quarks in a fast moving nucleus is not a simple convolution of 
their distributions within nucleons, known as the ``EMC 
effect''\cite{EMC_first} (for reviews on the extensive investigations, see  
\cite{EMC_CERN,EMC_SLAC,EMC_HERMES,EMC_JLab,EMC_John,EMC_mdeium_1,EMC_medium_2}).

A wealth of information on the structure of matter lies in the correlations 
between the momentum and spatial degrees of freedom of the partons. These 
correlations are set to be revealed through deeply virtual Compton scattering 
(DVCS), i.e., the hard exclusive lepto-production of a real photon, which 
provide access to a three-dimensional imaging of partons within the generalized 
parton distributions (GPDs) framework 
\cite{Mueller:1998fv,Ji:1996ek,Ji:1996nm,Radyushkin:1996nd,Radyushkin:1997ki}.   
The free proton DVCS measurement has been the focus of a worldwide effort 
\cite{Stepanyan:2001sm,Airapetian,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz 
Camacho:2006hx,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}
involving several accelerator facilities such as Jefferson Lab (JLab), HERA and  
CERN. Combining these measurements has enabled the first tomography extraction 
of the free proton \cite{Dupre:2016mai}. New groundbreaking measurements of 
exclusive DVCS from the $^{4}$He nucleus are a critical step towards providing 
similar 3D pictures of the quark structure of the nucleus as a whole, via the 
coherent channel \cite{Hattawy:2017woc}, and provide a new approach to 
understanding the partonic modifications of the bound nucleons via the 
incoherent DVCS channel \cite{simonetta_2,Guzey:2006xi,Guzey:2008fe}. The 
$^{4}$He nucleus is an ideal experimental target for these purposes as it has 
only one chiral-even GPD that parametrizes its partonic structure, is 
characterized by a strong binding energy, and has a relatively high nuclear 
core density. The inclusive scattering off $^{4}$He has shown a large EMC 
effect \cite{JSeely}, making this nucleus a golden target for investigating the 
medium partonic modifications.

@@

FIG.~\ref{fig:diags} illustrates a schematic representation of the 
leading-twist handbag diagram for the incoherent DVCS off $^{4}$He. In the 
Bjorken region, i.e, large virtual photon four-momentum squared 
($Q^{2}=-(k-k^\prime)^2$), and at small invariant momentum transfer ($t$), the 
DVCS handbag diagram can be factorized, leaving the non-perturbative structure 
of the nucleon to be parametrized in terms of four chirally-even GPDs: $H$, 
$E$, $\widetilde{H}$, and $\widetilde{E}$, representing the four helicity-spin 
combinations of the quark-nucleon states \cite{Freund_Collins,Ji_Osborne}.

In this Letter, we present the beam-spin asymmetries associated with the photon 
electroproduction on bound-proton off $^{4}$He. While the experimentally 
measured cross section amplitude is the sum of the DVCS, BH (i.e., the final 
state real photon is emitted by the incident or the scattered electron), and 
their interference, the beam-spin asymmetry observable is sensitive to the 
amplitudes that contain information on the GPDs, i.e., DVCS and interference 
amplitudes. The beam-spin asymmetry observable is measurable using a polarized 
lepton beam on unpolarized target (U) and defined in terms of the cross 
sections as
\begin{equation}
  A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
                {d^{5}\sigma^{+} + d^{5}\sigma^{-}}.
    \label{BSA_equation}
  \end{equation}
where $d^{5}\sigma^{+}$($d^{5}\sigma^{-}$) is the photon electroproduction 
differential cross section for a positive (negative) beam helicity.

Following the cross section decomposition suggested by \cite{Belitsky:2001ns}, 
the different amplitudes can be expressed in terms of Fourier coefficients 
associated with $\phi$-harmonics, where $\phi$ is the angle between the 
leptonic and the hadronic planes of the reaction. At leading-twist, the 
beam-spin asymmetry can be simplified as \begin{equation}
   A_{LU}(\phi) = \frac{a_{0}\sin(\phi)}{1+a_{1}\cos(\phi)+a_{2}\cos(2\phi)}
   \label{eq:alu-simp}
\end{equation}
with the parameters $a_{0,1,2}$ are combinations of the above mentioned Fourier 
coefficients. The first sine harmonic of the beam-spin asymmetry is dominant 
and proportional to the following combination of Compton form factors (CFF) 
\cite{Guidal:2013rya}
\begin{equation}
   A_{LU}^{\sin\phi} \propto \operatorname{Im}( F_1 \mathcal{H}- \frac{t}{4M^2} 
   F_2 \mathcal{E}+ \frac{x_B}{2}(F_1+F_2)\tilde{\mathcal{H}})
\end{equation}
where $F_1$ and $F_2$ are the Dirac and Pauli form factors with $x_B$ as the 
Bjorken scaling variable. The real and the imaginary parts of the CFF 
$\mathcal{H}$ are corresponding to the GPD $H$ by  \begin{align}
   \Re(&\mathcal{H}) = \mathcal{P} \int_{0}^{1}dx[H(x,\xi,t)-H(-x,\xi,t)] \, 
   C^{+}(x,\xi) \\
   \Im(&\mathcal{H}) = - \pi [H(\xi,\xi,t)-H(-\xi,\xi,t)],
\end{align}
with $\mathcal{P}$ is the Cauchy principal value integral and $C^{+}$ is a 
coefficient function defined as $(1/(x-\xi) + 1/(x+\xi))$ with $\xi$ being 
related to $x_B$ by $\xi\approx {{x_B}\over{2-x_B}}$. Similar expressions apply 
for the GPDs $E$, $\widetilde{H}$, and $\widetilde{E}$.

@@

The experiment (E08-024~\cite{Hafidi:2008pr}) took place in Hall-B of Jefferson 
Lab using the nearly 100\% duty factor, longitudinally-polarized electron beam 
(83$\%$ polarization) from the Continuous Electron Beam Accelerator Facility 
(CEBAF) accelerator at its full energy of 6.064 GeV. The data were accumulated 
over 40 days using a 6-atm-pressure, 292-mm-long, and 6-mm-diameter gaseous 
$^4$He target centered at 64~cm upstream of the CEBAF Large Acceptance 
Spectrometer (CLAS) center. For similar DVCS experiments on free-proton target
\cite{Girod:2007aa,Jo:2015ema}, the CLAS baseline design \cite{Mecking:2003zu} 
is supplemented with an inner calorimeter (IC) and a solenoid. The IC extends 
the photon detection acceptance of CLAS, which was originally from 15$^{\circ}$ 
to 45$^{\circ}$, to polar angles as low as 4$^{\circ}$. As the coherent DVCS 
off $^4$He, where the nucleus remain intact, was one of the proposed 
measurements of our experiment and since CLAS cannot detect such low-energy 
recoil nuclei, we built a small radial time projection chamber (RTPC) around 
the target cell. (See~\cite{Dupre:2017upj} for a detailed description of the 
RTPC and its performances and \cite{Hattawy:2017woc} for the coherent DVCS 
measurements). In this setup, the 5-Tesla solenoid (that surrounds the target 
and the RTPC) enabled the detection of the low-energy charged ions in the RTPC 
and prevented the high-rate low-energy M\o{}ller electrons from reaching CLAS 
sub-detectors by guiding these electrons towards a heavy shield placed around 
the beam line.

% DVCS selection
Incoherent DVCS events were selected if an electron, a proton, and at least one 
photon were detected in the final state. Electrons were identified by having 
appropriate deposited energy in the electromagnetic calorimeter and proper 
light yield in the Cherenkov counters in addition to having a negative 
track-curvature in the drift chambers that corresponds to a momentum greater 
than 800 MeV. The protons were distinguished from other positive particles by 
timing cuts established using the time-of-flight measured by the scintillators 
and the reconstructed track information from the drift chambers. Also, the 
selected proton was required to be originating from the electron's vertex by 
applying a vertex matching cut. The photons were detected in either the IC or 
the CLAS electromagnetic calorimeter. All the signals within IC fiducial region 
were assumed to be photons, while a timing cut is used to clean the EC photons 
from neutrons. Note that even though the DVCS reaction has only one real photon 
in the final state, events with more than one good photon are not discarded at 
this stage. It was observed by the DVCS exclusivity cuts, discussed below, that 
most of these photons are soft ones produced in random coincidence. In the 
following selection stage, the most energetic photon is considered as the DVCS 
photon candidate (see \cite{Hattawy:thesis} for additional details on the 
particles identification).

Further requirements were applied to clean the identified initial set of 
incoherent DVCS events from backgrounds and other channels. Events were 
selected with $Q^{2}$ greater the 1 GeV$^2$ to ensure that the interaction 
occurs at the partonic level and the applicability of the factorization on the 
DVCS handbag diagram, $\gamma^{*}p$ invariant mass (W) greater than 2 GeV to 
avoid the nucleon region of excitation to resonances, and the transferred 
momentum squared to the recoil proton has to be greater than a
minimum value defined by the kinematics of the beam and the scattered electron 
($-t~>~-t_{min}$). Then, the exclusivity of the incoherent DVCS events was 
ensured by imposing constraints on the kinematical variables resulting from 
conserving the four-momentum in the reaction $ep\rightarrow e'p'\gamma$. These 
kinematical variables are: the coplanarity angle $\Delta\phi$ between the 
($\gamma,\gamma^*$) and ($\gamma^*$,$p'$) planes, the missing energy, mass, and 
transverse momentum of the $e'\gamma$ and $e'p'\gamma$ system, the missing mass 
squared of the $e'p'$ system, and the angle $\theta$ between the measured 
photon and the missing momentum of the $e'p'$ system. The experimental data for 
the most relevant exclusivity variables and applied cuts are shown in 
FIG.~\ref{fig:kin-cuts} (see \cite{Hattawy:thesis} for additional details). We 
also rejected events where a $\pi^0$ was identified by the invariant mass of 
two photons. About 30k events passed all these requirements; their kinematic 
distributions are shown in FIG.~\ref{fig:kin-coverage}.

@@

%background
In spite of our selection requirements, two main backgrounds were observed to 
contaminate our incoherent DVCS sample; accidental coincidences and exclusive 
$\pi^0$ production. For the accidental events, i.e., $e'p'\gamma$ collection 
with particles originated from different events, their contribution of 6.5\% 
was evaluated by selecting events passing all our cuts but originating from 
different vertices. Regarding the $\pi^0$ contamination, i.e., $ep\rightarrow 
e'p'\pi^0$ events where one of the two photons of the $\pi^0$ decay is produced 
below the energy threshold or outside the detection acceptance, we evaluated 
this contribution by using data and simulation. From the simulation, we 
calculated the ratio ($R$) between the number of $\pi^0$ events where the two 
photons are detected and those that would be mistaken for DVCS ($R = 
N^{1\gamma}_{sim}/N^{2\gamma}_{sim}$). Then in each kinematical bin and for 
each beam-helicity state, the $\pi^0$-subtracted experimental DVCS events is 
calculated as $N = N^{ep\rightarrow e'p'\gamma}_{exp}- R~N^{ep\rightarrow 
e'p'\pi^0}_{exp}$, where $N^{ep\rightarrow e'p'\gamma}_{exp}$ is the 
experimentally identified number of $ep\rightarrow e'p'\gamma$ and 
$N^{ep\rightarrow e'p'\pi^0}_{exp}$ is the experimentally identified 
$ep\rightarrow e'p'\pi^0$ with the two photons were detected. Depending on the 
kinematics, we found contaminations of 8\%-10\%.

%asymmetries
It is convenient to use the beam-spin asymmetry as a DVCS observable because  
the cross sections luminosity normalization and detector efficiencies cancel 
out in the asymmetry ratio.  Experimentally, $A_{LU}$ can be simplified in 
terms of the reaction yield in each beam-helicity state ($N^{\pm}$) as
\begin{equation}
A_{LU} = \frac{1}{P_{B}} \frac{N^{+} - N^{-}}{N^{+} + N^{-} }.
\end{equation}
where $P_{B}$ is the longitudinal beam polarization.

Following the model guidance of \cite{Guidal:2013rya}, the GPD $H$ dominants 
the other three GPDs within the accessible phase-phase of using the 6 GeV 
electron beam from CEBAF and CLAS spectrometer. Therefore, measuring $A_{LU}$ 
gives access to the real and imaginary part of the CFF $\mathcal{H}$ through 
the parameters $a_0$, $a_1$, and $a_2$ of equation \ref{eq:alu-simp}.  
Moreover, the free proton $A_{LU}$ measurements, \cite{Girod:2007aa}, have 
shown that the $cos(2\phi)$ term, which is corresponding to the pure DVCS 
amplitude, is suppressed and compatible with zero.

Due to limited statistics, the data were binned two-dimensionally into 36 bins.  
That is, four statistically-equivalent bins in each of the kinematical 
variables ($Q^{2}$, $x_{B}$, $t$) were constructed one at a time. Then, each 
bin is divided into nine bins in the azimuthal angle ($\phi$).  
FIG.~\ref{fig:alu} presents the measured incoherent $A_{LU}$ as a function of 
$\phi$ in bins in $Q^{2}$, $x_{B}$, and $t$. The curves on the plots are fits 
of the approximated form $\frac{a_{0}~sin(\phi)}{1+ a_{1}~cos(\phi)}$. The 
study of systematic uncertainties showed that the main contributions come from 
the choice of the DVCS exclusivity cuts (6\%) and the large binning size (7\%).  
However, added quadratically, these uncertainties sum up to about 10\%, which 
always remains significantly smaller than the statistical errors.

@@

We present in FIG.~\ref{fig:alu90} the dependence of the fitted $A_{LU}$ 
signals at $\phi$~=~90$^{\circ}$ on the kinematical variables $Q^2$, $x_{B}$, 
and $t$. Within the given uncertainties, $A_{LU}$ does not indicate a strong 
dependence on $Q^2$. The $x_{B}$ and $t$ dependencies are compared to 
theoretical calculations performed by S.~Liuti and K.~Taneja 
\cite{simonetta_2}. Their model uses a realistic spectral function and 
considers off-shell effects. The calculations are carried out at slightly 
different kinematics than our data but still provide some guidance. The 
experimental results appear to have smaller asymmetries than the calculations.  
These differences may arise from nuclear effects which are not taken into 
account in the model, such as long-range interactions.

@@

The $A_{LU}$ ratios show a 20\%-40\% suppression in the bound protons compared 
to the free protons. These measurements disagree with the enhancement predicted 
by the on-shell calculations that use the medium modified GPDs as caluclated 
from the quark-meson coupling model \cite{Guzey:2008fe}. The off-shell 
calculations overshoot the data indicating a trend \cite{simonetta_2}. In
particular, the anti-shadowing region seems to be absent in terms of the 
$A_{LU}$ ratio, while it was predicted by the calculation. Within the given 
uncertainties, our measured ratios are compatible with the previous measured 
single point from HERMES \cite{Airapetian}.

These data, while limited in statistics, proved the experimental feasibility of 
measuring DVCS of bound-nucleons in addition to the EMC effect within the GPDs 
framework and led the way to the approval of a next generation nuclear 
measurements \cite{Armstrong:2017wfw}. The future measurements will be carried 
out using the new CLAS12 spectrometer and the upgraded CEBAF 12 GeV electron 
beam at an electron-nucleon luminosity of 10$^{35}$cm$^{-2}$s$^{-1}$. The wider 
accessible phase-space and the higher luminosity will enable us to study 
nuclear effects and their manifestations on GPDs including the effect of final 
state interactions.

%conclusion
In summary, we have presented the first exclusive beam-spin asymmetries 
associated with incoherent DVCS off $^4$He using an upgraded setup of CLAS 
spectrometer at Jefferson Lab. Our results were compared to some model 
calculations based on different assumptions of the nuclear medium effects at 
the partonic level and allowed us to draw some conclusions. The bound-proton 
beam-spin asymmetries indicate a suppression compared to the free proton 
results measured in similar phase-space. While the data are limited in 
statistics, they opened new insights for extensive future measurements.

>>>>

%
\begin{document}
\linenumbers

\title{First exclusive DVCS measurement off bound nucleon in $^4$He}
%\title{Revealing the Bound Nucleon 3D Partonic Structure through Incoherent Deeply Virtual Compton Scattering off $^4$He}

@@

%
\date{\today}
\begin{abstract}
We report on the beam-spin asymmetries associated with incoherent deeply 
   virtual Compton scattering off $^4$He in the valence quark region. The data 
   were accumulated using a 6 GeV longitudinally-polarized electron beam 
   incident on a pressurized $^4$He gaseous target placed in front of the CLAS 
   spectrometer in Hall-B at the Thomas Jefferson National Accelerator 
   Facility.  The baseline detection sub-systems of CLAS detected the scattered 
   electrons and the recoil protons, while the final-state real photons are 
   detected by a supplementary electromagnetic calorimeter at very forward 
   angles. The measured beam-spin asymmetries on bound-protons exhibit a 
   suppression compared to those on free proton, indicating possible medium 
   modifications on the nucleon's quark distributions and opening new 
   opportunities to explore the origin of the EMC effect within the framework 
   of the generalized parton distributions.

@@

Electromagnetic probes have played a major role in advancing our knowledge 
about the structure of nucleons, which are the origin of almost all the
Universe's visible matter. While elastic lepton-nucleon measurements have 
taught us about the spatial charge and magnetization distributions 
\cite{Hofstadter:1955ae,Perdrisat:2006hj}, deep-inelastic scattering (DIS) 
experiments have uncovered the features of momentum sharing between the 
constituents partons, i.e., quarks and gluons \cite{Dokshitzer:1977sg,pdg}.  
With nuclear targets, the DIS measurements have revealed the fact that the 
distribution of quarks in a fast moving nucleus is not a simple convolution of 
their distributions within nucleons, an observation known as the ``EMC 
effect''\cite{EMC_first} (for reviews on the extensive investigations, see  
\cite{EMC_CERN,EMC_SLAC,EMC_HERMES,EMC_JLab,EMC_John,EMC_mdeium_1,EMC_medium_2}).

A wealth of information on the structure of matter lies in the correlations 
between the momentum and spatial degrees of freedom of the partons. These 
correlations are set to be revealed through deeply virtual Compton scattering 
(DVCS), i.e., the hard exclusive lepto-production of a real photon, which 
provides access to a three-dimensional imaging of partons within the 
generalized parton distributions (GPDs) framework 
\cite{Mueller:1998fv,Ji:1996ek,Ji:1996nm,Radyushkin:1996nd,Radyushkin:1997ki}.   
The free proton DVCS measurement has been the focus of a worldwide effort 
\cite{Stepanyan:2001sm,Airapetian:2001yk,Airapetian:2006zr,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz 
Camacho:2006hx,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}
involving several accelerator facilities such as Jefferson Lab, HERA and  
CERN. Combining these measurements has enabled the first extractions of GPDs 
and a 3-D tomography of the free proton \cite{Guidal:2013rya,Dupre:2016mai}.  
New measurements of exclusive DVCS from the $^{4}$He nucleus are a critical 
step towards providing similar 3-D pictures of the quark structure of the 
nucleus as a whole, via the coherent channel 
\cite{Airapetian:2009cga,Hattawy:2017woc}, and provide a new approach for 
understanding modifications of the partonic structure of the bound nucleons via 
the incoherent DVCS channel \cite{simonetta_2,Guzey:2006xi,Guzey:2008fe}. The 
$^{4}$He nucleus is an ideal experimental target for these purposes as it has 
only one chiral-even GPD that parametrizes its partonic structure, is 
characterized by a strong binding energy, and has a relatively high nuclear 
core density. The inclusive scattering off $^{4}$He has shown a large EMC 
effect \cite{JSeely}, making this nucleus a golden target for investigating the 
medium modifications of the nucleon's partonic structure.

@@

FIG.~\ref{fig:diags} illustrates the 
leading-twist handbag diagram for the incoherent DVCS off $^{4}$He. In the 
Bjorken regime, i.e, large virtual photon four-momentum squared 
($Q^{2}=-q^2=-(k-k^\prime)^2$), and at small invariant momentum transfer ($t=(p-p^\prime)^2$), the 
DVCS scattering process can be factorized, leaving the non-perturbative structure 
of the nucleon to be parametrized in terms of four chirally-even GPDs: $H$, 
$E$, $\widetilde{H}$, and $\widetilde{E}$, representing the four helicity-spin 
combinations of the quark-nucleon states \cite{Freund_Collins,Ji_Osborne}.

In this Letter, we present the first exclusive measurement of the beam-spin asymmetry in deeply virtual electroproduction of a real photon off bound-proton in $^{4}$He. Experimentally we measure squared sum of the Bethe-Heitler (BH) and DVCS amplitudes, with BH process where real photon is emitted by the incident or the scattered electron dominating the cross section in our kinematics.   
%While the experimentally measured cross section amplitude is the sum of the DVCS, BH (i.e., the final state real photon is emitted by the incident or the scattered electron), and their interference, 
The beam-spin asymmetry, in other hand, is sensitive to the DVCS amplitude and the interference term that contain information on the GPDs. 
The beam-spin asymmetry observable with a longitudinally polarized electron beam (L) and unpolarized target (U) is defined as:
\begin{equation}
  A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
                {d^{5}\sigma^{+} + d^{5}\sigma^{-}}.
    \label{BSA_equation}
  \end{equation}
where $d^{5}\sigma^{+}$($d^{5}\sigma^{-}$) is the photon electroproduction 
differential cross section for a positive (negative) beam helicity.

Following the cross section decomposition provided in \cite{Belitsky:2001ns}, 
the different components can be expressed in terms of Fourier coefficients 
associated with $\phi$-harmonics, where $\phi$ is the angle between the 
leptonic and the hadronic planes of the reaction. At leading-twist, the 
beam-spin asymmetry can be simplified as: 
\begin{equation}
   A_{LU}(\phi) = \frac{a_{0}\sin(\phi)}{1+a_{1}\cos(\phi)+a_{2}\cos(2\phi)}
   \label{eq:alu-simp}
\end{equation}
where the parameters $a_{0,1,2}$ are combinations of the above mentioned Fourier 
coefficients. The $\sin(\phi)$ harmonic is dominant in $A_{LU}$ 
and is proportional to the following combination of Compton form factors (CFF) 
\cite{Guidal:2013rya}
\begin{equation}
   A_{LU}^{\sin\phi} \propto \operatorname{Im}( F_1 \mathcal{H}- \frac{t}{4M^2} 
   F_2 \mathcal{E}+ \frac{x_B}{2}(F_1+F_2)\tilde{\mathcal{H}})
\end{equation}
where $F_1$ and $F_2$ are the Dirac and Pauli form factors with $x_B$ as the 
Bjorken scaling variable. The real and the imaginary parts of the CFF 
$\mathcal{H}$ relate to the GPD $H$ as  
\begin{align}
   \Re(&\mathcal{H}) = \mathcal{P} \int_{0}^{1}dx[H(x,\xi,t)-H(-x,\xi,t)] \, 
   C^{+}(x,\xi) \\
   \Im(&\mathcal{H}) = - \pi [H(\xi,\xi,t)-H(-\xi,\xi,t)],
\end{align}
with $\mathcal{P}$ is the Cauchy principal value integral and $C^{+}$ is a 
coefficient function defined as $(1/(x-\xi) + 1/(x+\xi))$ with $\xi$ being 
related to $x_B$ by $\xi\approx {{x_B}\over{2-x_B}}$. Similar expressions apply 
for the GPDs $E$, $\widetilde{H}$, and $\widetilde{E}$.

@@

The experiment (E08-024~\cite{Hafidi:2008pr}) took place in Hall-B of Jefferson 
Lab using the nearly 100\% duty factor, longitudinally-polarized electron beam 
(83$\%$ polarization) from the Continuous Electron Beam Accelerator Facility 
(CEBAF) accelerator at energy of 6.064 GeV. The data were accumulated 
over 40 days using a 6-atm-pressure, 292-mm-long, and 6-mm-diameter gaseous 
$^4$He target centered at 64~cm upstream of the CEBAF Large Acceptance 
Spectrometer (CLAS) coordinate center. For similar DVCS experiments on free-proton target
\cite{Girod:2007aa,Jo:2015ema}, the CLAS baseline design \cite{Mecking:2003zu} 
is supplemented with an inner calorimeter (IC) and a solenoid magnet. The IC extends 
the photon detection acceptance of CLAS to very small polar angles, 4$^{\circ}$. 
%As the coherent DVCS off $^4$He, where the nucleus remain intact, was one of the proposed measurements of our experiment and since CLAS cannot detect such low-energy recoil nuclei, we built a small radial time projection chamber (RTPC) around the target cell. (See~\cite{Dupre:2017upj} for a detailed description of the RTPC and its performances and \cite{Hattawy:2017woc} for the coherent DVCS measurements). In this setup, 
The 5-Tesla solenoid magnet in the center of which target was located 
%(that surrounds the target and the RTPC) enabled the detection of the low-energy charged ions in the RTPC and 
prevented the high-rate low-energy M{\o}ller electrons from reaching the CLAS drift chambers by guiding them electrons insde a tungsten shield placed around the beam line.

% DVCS selection
Incoherent DVCS events were selected if an electron, a proton, and at least one 
photon were detected in the final state. Electrons were identified as negatively charged tracks reconstructed in drift chambers with an appropriate energy deposition in the electromagnetic calorimeters (EC) and a proper 
light yield in the Cherenkov counters. The protons were identified from positively charged tracks by 
timing analysis using the time-of-flight measured by the scintillator counters. 
In addition, it was required that both the electron and the proton in the event originated from the same vertex at the target within CLAS tracking vertex resolution. The photons were detected in either the IC or 
the CLAS electromagnetic calorimeters. All the clusters within the IC fiducial region 
were assumed to be photons, while a timing cut is used to clean the EC photons 
from neutrons. Note that even though the DVCS reaction has only one real photon 
in the final state, events with more than one photon were not discarded at 
this stage. As will be discussed below, the DVCS exclusivity cuts allow identification of the correct photon in the event, discarding accidental, mostly soft photons. In the following selection stage, the most energetic photon is considered as the DVCS 
photon candidate (see \cite{Hattawy:thesis} for additional details on the particles identification).

Further requirements were applied to clean the identified initial set of 
incoherent DVCS events from accidental and physics background events. First, events were 
selected with Q$^{2}$ greater the 1 GeV$^2$ to ensure the applicability of the 
DVCS handbag diagram, and with $\gamma^{*}p$ invariant mass (W$=(q+p)^2$) greater than 2 GeV to 
avoid the nucleon resonance region. The transferred momentum squared to the recoil proton was required to be greater than a
minimum allowed value at given Q$^2$ and W ($t~>~t_{min}$). Then, the exclusivity of the incoherent DVCS events was 
ensured by imposing constraints on the kinematical variables resulting from 
conserving the four-momentum in the reaction $ep\rightarrow e'p'\gamma$. These 
kinematical variables are: the coplanarity angle $\Delta\phi$ between the 
($\gamma,\gamma^*$) and ($\gamma^*$,$p'$) planes, the missing energy, mass, and 
transverse momentum of the $e'\gamma$ and $e'p'\gamma$ systems, the missing mass 
squared of the $e'p'$ system, and the angle $\theta$ between the measured 
photon and the missing momentum of the $e'p'$ system. The experimental data for 
the most relevant exclusivity variables and applied cuts are shown in 
FIG.~\ref{fig:kin-cuts} (see \cite{Hattawy:thesis} for additional details). We 
also rejected events where a $\pi^0$ was identified by the invariant mass of 
two photons. About 30k events passed all these requirements; their kinematic 
distributions are shown in FIG.~\ref{fig:kin-coverage}.

@@

%background
The two main backgrounds that contribute to the event sample after the exclusivity cuts are  
events due to accidental coincidences and exclusive $\pi^0$ production where one of photons from $\pi^0$ decay escape the detection. For the accidental events, i.e., $e'p'\gamma$ collection 
with particles originated from different electron scattering events, their contribution of 6.5\% 
was evaluated by selecting events passing all our cuts but originating from 
different vertices. The $\pi^0$ contamination 
%, i.e., $ep\rightarrow e'p'\pi^0$ events where one of the two photons of the $\pi^0$ decay is produced below the energy threshold or outside the detection acceptance, we
was estimated 
%this contribution by 
using the data and simulation. From simulation, we 
calculated the ratio ($R$) of the number of $\pi^0$ events that are identified as $ep\rightarrow e'p'\gamma$ events after our selection cuts to the number of identified $\pi^0$ events, $R = N^{1\gamma}_{sim}/N^{2\gamma}_{sim}$. Then in each kinematical bin and for 
each beam-helicity state, the $\pi^0$-subtracted experimental DVCS events is 
calculated as $N = N^{ep\rightarrow e'p'\gamma}_{exp}- R~N^{ep\rightarrow 
e'p'\pi^0}_{exp}$, where $N^{ep\rightarrow e'p'\gamma}_{exp}$ is the 
experimentally identified number of $ep\rightarrow e'p'\gamma$ and 
$N^{ep\rightarrow e'p'\pi^0}_{exp}$ is the experimentally identified 
$ep\rightarrow e'p'\pi^0$ with the two photons were detected. Depending on the 
kinematics, we found contaminations of 8\%-10\%.

%asymmetries
%It is convenient to use the beam-spin asymmetry as a DVCS observable because  the cross sections luminosity normalization and detector efficiencies cancel out in the asymmetry ratio.  
Experimentally, $A_{LU}$ 
%can be simplified in terms of the reaction yield in each beam-helicity state ($N^{\pm}$) 
is defined as
\begin{equation}
A_{LU} = \frac{1}{P_{B}} \frac{N^{+} - N^{-}}{N^{+} + N^{-} }.
\end{equation}
where $N^{+}$ and $N^{-}$ are the number of DVCS events for positive and negative  beam-helicity state, and $P_{B}$ is the longitudinal beam polarization.

In the kinematical domain of our experiment, the dominant contribution to the beam-spin asymmetry comes from GPD H \cite{Guidal:2013rya} and
%Following the model guidance of \cite{Guidal:2013rya}, the GPD $H$ dominants the other three GPDs within the accessible phase-phase of using the 6 GeV electron beam from CEBAF and CLAS spectrometer. Therefore, 
therefore $\phi$ dependence of $A_{LU}$ gives access to the real and imaginary part of the CFF $\mathcal{H}$ through 
the parameters $a_0$, $a_1$, and $a_2$ of equation \ref{eq:alu-simp}. The studies of  
the free proton $A_{LU}$ measurements, \cite{Girod:2007aa}, have 
shown that the the pure DVCS contribution, $cos(2\phi)$ term ($a_2$), is suppressed and compatible with zero.

Due to limited statistics, the data were binned two-dimensionally into 36 bins.  
That is, four statistically-equivalent bins in each of the kinematical 
variables ($Q^{2}$, $x_{B}$, $t$) were constructed one at a time. Then, each 
bin is divided into nine bins in the azimuthal angle ($\phi$).  
FIG.~\ref{fig:alu} presents the measured incoherent $A_{LU}$ as a function of 
$\phi$ in bins of $Q^{2}$, $x_{B}$, and $t$. The curves on the plots are fits 
of the approximated form $\frac{a_{0}~sin(\phi)}{1+ a_{1}~cos(\phi)}$. The 
study of systematic uncertainties showed that the main contributions come from 
the choice of the DVCS exclusivity cuts (6\%) and the large binning size (7\%).  
Added quadratically, these uncertainties sum up to less than 10\% for all data points and are significantly smaller than the statistical errors.

@@

We present in FIG.~\ref{fig:alu90} the dependence of the fitted $A_{LU}$ 
signals at $\phi$~=~90$^{\circ}$ on the kinematical variables $Q^2$, $x_{B}$, 
and $t$. Within the given uncertainties, $A_{LU}$ does not indicate a strong 
dependence on $Q^2$. The $x_{B}$ and $t$ dependencies are compared to 
theoretical calculations performed by S.~Liuti and K.~Taneja 
\cite{simonetta_2}. Their model uses a realistic spectral function and 
considers off-shell effects. The calculations are carried out at slightly 
different kinematics than our data but still provide important guidance. The 
experimental results appear to have smaller asymmetries than the calculations.  
These differences may arise from nuclear effects which are not taken into 
account in the model, such as long-range interactions. On the graph for $t$ dependence we show previous measurements by  the HERMES collaboration  \cite{Airapetian} using inclusive final state, ($e^\prime\gamma$). Due to large experimental uncertainties of HERMES points, the only conclusion is that the two measurements do not disagree.

@@

The $A_{LU}$ ratios show a 20\%-40\% lower asymmetries for a bound proton compared 
to the free proton. The measurements disagree with the off-shell \cite{simonetta_2} and the on-shell calculations that use the medium modified GPDs as calculated from the quark-meson coupling model \cite{Guzey:2008fe}.
%the enhancement predicted by the on-shell calculations that use the medium modified GPDs as calculated from the quark-meson coupling model \cite{Guzey:2008fe}. The off-shell calculations overshoot the data indicating a trend \cite{simonetta_2}. 
In particular, the anti-shadowing region where off-shell model expects enhancement of the ratio experiment shows a sharp drop. Within the given 
uncertainties, our measured ratios are compatible with the previously measured 
single point from HERMES \cite{Airapetian}.

%These data, while limited in statistics, proved the experimental feasibility of measuring DVCS of bound-nucleons in addition to the EMC effect within the GPDs framework and led the way to the approval of a next generation nuclear measurements \cite{Armstrong:2017wfw}. The future measurements will be carried out using the new CLAS12 spectrometer and the upgraded CEBAF 12 GeV electron beam at an electron-nucleon luminosity of 10$^{35}$cm$^{-2}$s$^{-1}$. The wider accessible phase-space and the higher luminosity will enable us to study nuclear effects and their manifestations on GPDs including the effect of final state interactions.
